|

### 2021-03-17 documentation/readme.Rmd
Fixed minor error in README
Add hex sticker to README
Fixed issue with Cabin font and minor formatting issue in README

@@

``` r
devtools::install_github("jackobailey/britpol")

@@

{britpol}, `pollbase`, and `pollbasepro` will change over time as elections come and go. Users should use only the most recent version of the package when conducting their analyses. Like any project, some minor mistakes might have crept into the code. If you think that you have found an error or would like to make a recommendation for a future update, please [raise an issue](https://github.com/jackobailey/britpol/issues).

>>>>

<img src="https://raw.githubusercontent.com/jackobailey/britpol/master/documentation/_assets/hex.png" alt="The britpol hexlogo" align="right" width="200" style="padding: 0 15px; float: right;"/>

@@

``` r
devtools::install_github("jackobailey/britpol")
```

@@

`{britpol}`, `pollbase`, and `pollbasepro` will change over time as elections come and go. Users should use only the most recent version of the package when conducting their analyses. Like any project, some minor mistakes might have crept into the code. If you think that you have found an error or would like to make a recommendation for a future update, please [raise an issue](https://github.com/jackobailey/britpol/issues).
